Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.8)} \underline{Drafting Committee: DC90 (\today)}

### 2011-03-01 background_and_systematic.tex
updated background_and_systematic

\section{Background Corrections and Systematic Uncertainties}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, 
shifts in the missing-mass event distributions and various detector and binning
effects determined as in Refs.~\cite{Air08,Air09}. The
1996-2005 elastic sample also has a systematic uncertainty from misalignment of the spectrometer, which has been eliminated for the 2006-2007 data sample. Contributions to the uncertainties on the amplitude measurements arise from background in the data from events that include neutral meson production. The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607} \blue{for the amplitudes extracted in a single bin in the H{\sc ermes} kinematic region}.

Another contribution to the systematic uncertainty comes from the relative shift of the
missing-mass distributions between the electron and positron data
samples~\cite{Zei09,Bur10}. The exclusive region in the missing-mass
distribution is adjusted for each calorimeter calibration period for data
collected in 2007 to account for the observed time dependence. One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty. The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
which is present in the beam-helicity amplitudes and is quoted as an
independent scale uncertainty.

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. \blue{An event
generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation} because it describes the data well and to keep consistency with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data. In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. These contributions are summarised in Table
\ref{table_systematic_contributions_0607}.

\blue{The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state. As the recoiling proton is not detected, separation of the latter events from rest of the data sample is not possible due to the experimental technique.}
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``\blue{A}ssoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform the estimation is described in detail in
Ref.~\cite{Air08}.

\begin{table}[H]
 \begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
 & $A$ $\pm \delta_{stat.}$ $\pm \delta_{syst.}$ & Background & Missing-Mass Shift & Detector Effects & & Total \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.209  $\pm$  0.026  $\pm$   0.026 & 0.005 & 0.005 & 0.025 & & 0.026 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & -0.015  $\pm$  0.026  $\pm$  0.008 & 0.004 & 0.007 & 0.001 & & 0.008 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.025  $\pm$   0.005 & 0.005 & 0.001 & 0.002 & & 0.006 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.039 $\pm$  0.004 $\pm$  0.008 & 0.001 & 0.004 & 0.007 & & 0.008 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.003 & 0.002 & 0.001 & 0.002 & & 0.003 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.007  $\pm$  0.006  $\pm$   0.002 & 0.001 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.009  $\pm$   0.006   $\pm$   0.001 & 0.000 & 0.001 & 0.001 & & 0.001 \\
  \hline
 \end{tabular}
}
  \caption{The contributions to \blue{the} systematic uncertainty due to the
background correction, the time-dependen\blue{t shifts} of the missing-mass
distributions and detector effects for the 2006-2007 data to the total
systematic uncertainty. The total systematic uncertainties, shown in the
right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

>>>>

\section{Background Corrections and Systematic Uncertainties}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, 
shifts in the missing-mass distributions and various detector and binning
effects determined as in Refs.~\cite{Air08,Air09}. Contributions to the uncertainties on the amplitude measurements arise from background in the data from neutral meson production. The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607} for the amplitudes extracted in a single bin in the H{\sc ermes} kinematic region.

Another contribution to the systematic uncertainty comes from the relative shift of the
missing-mass distributions. \blue{There are shifts in the distributions for electron and positron data~\cite{Zei09,Bur10}}. \blue{The missing-mass
distribution is also adjusted for each calorimeter calibration period of data
collected in 2007 to account for the observed time dependence.} One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty. The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
which is present in the beam-helicity amplitudes and is quoted as an
independent scale uncertainty.

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. An event
generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation because it describes the data well and is consistent with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data. In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. 
\blue{The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer, 
which has been eliminated for the 2006-2007 data sample.}
These contributions are summarised in Table
\ref{table_systematic_contributions_0607}.

The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state. \blue{The} recoiling proton is not detected \blue{and the calorimeter resolution does not allow}, separation of the latter events from rest of the data sample is not possible due to the experimental technique.
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation \blue{from} Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``Assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform \blue{this} estimation is described in detail in
Ref.~\cite{Air08}.

\begin{table}[H]
 \begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$ $\pm$ $\delta_{syst.}$ & Background & Missing-Mass Shift & Detector Effects & & Total \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.209  $\pm$  0.026  $\pm$   0.026 & 0.005 & 0.005 & 0.025 & & 0.026 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & -0.015  $\pm$  0.026  $\pm$  0.008 & 0.004 & 0.007 & 0.001 & & 0.008 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.025  $\pm$   0.005 & 0.005 & 0.001 & 0.002 & & 0.006 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.039 $\pm$  0.004 $\pm$  0.008 & 0.001 & 0.004 & 0.007 & & 0.008 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.003 & 0.002 & 0.001 & 0.002 & & 0.003 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.007  $\pm$  0.006  $\pm$   0.002 & 0.001 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.009  $\pm$   0.006   $\pm$   0.001 & 0.000 & 0.001 & 0.001 & & 0.001 \\
  \hline
 \end{tabular}
}
  \caption{The contributions to the systematic uncertainty due to the
background correction, the time-dependent shifts of the missing-mass
distributions and detector effects for the 2006-2007 data to the total
systematic uncertainty. The total systematic uncertainties, shown in the
right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}
